Children's Books

### 2024-11-29 paper/paper.qmd
fixed alignment issues with references in pdf file

---
title: "Children's Books"
subtitle: "What factors influence the likelihood of a book being high-rated"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (Cookson 2020). By using a Bayesian logistic regression, I analyzed how various book characteristics impact the likelihood of a book receiving a high rating. The results showed that the book's cover type had the biggest positive impact on the likelihood of a book being high-rated. The insight from this research not only clarify the key elements of high-rated children's books, but also enhance future authors to push the boundaries of their literature by exploring different writing choices to enhance reader engagement."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: tbl-cleaned-dataset-preview
#| tbl-cap: "Preview of the Cleaned Children's Book Dataset"
#| message: false
#| echo: false
#| warning: false

@@

```{r}
#| message: false
#| echo: false
#| warning: false

@@

```{r}
#| label: tbl-summary-statistic
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-most-common-covers
#| fig-cap: "Proportion of High-rated Books by Cover Type"
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-page-count
#| fig-cap: "Average Page Counts of High-rated and Low-rated Books"
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-publish-year
#| fig-cap: "Number of Books by Publish Year and Rating Status"
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-rating-count
#| fig-cap: "Rating Counts by the Rating of the Book"
#| echo: false
#| warning: false

@@

```{r}
#| label: tbl-book-model
#| tbl-cap: "Modeling the likelihood of a book being High-rated"
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-distribution
#| fig-cap: "Posterior predictive check"
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-post-prior
#| fig-cap: "Comparison of the prior and posterior"
#| echo: false
#| warning: false
#| 
analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
model_file <- readRDS(file = here::here("models/model.rds"))

@@

```{r}
#| label: fig-trace
#| fig-cap: "Trace plot"
#| echo: false
#| fig-subcap: ["Intercept", "pages", "rating_count", "publish_year", "coverEbook", "coverKindle", "coverBoard", "coverHardcover", "coverPaperback"]
#| layout-ncol: 3
#| warning: false

@@

```{r}
#| label: fig-rhat
#| fig-cap: "Rhat Plot"
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-interval
#| fig-cap: "90% Credibility Intervals for Predictors of High-rated Books"
#| echo: false
#| warning: false

>>>>

---
title: "Children's Books"
subtitle: "What factors influence the likelihood of a book being high-rated"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (Cookson 2020). By using a Bayesian logistic regression, I analyzed how various book characteristics impact the likelihood of a book receiving a high rating. The results showed that the book's cover type had the biggest positive impact on the likelihood of a book being high-rated. The insight from this research not only clarify the key elements of high-rated children's books, but also enhance future authors to push the boundaries of their literature by exploring different writing choices to enhance reader engagement."
format:
  pdf:
    fig.pos: "H"
toc: true
number-sections: true
bibliography: references.bib
---

@@

```{r,  fig.pos: "H"}
#| label: tbl-cleaned-dataset-preview
#| tbl-cap: "Preview of the Cleaned Children's Book Dataset"
#| message: false
#| echo: false
#| warning: false

@@

```{r, fig.pos: "H"}
#| message: false
#| echo: false
#| warning: false

@@

```{r,  fig.pos: "H"}
#| label: tbl-summary-statistic
#| fig-cap: "Summary Statistic of the Dataset"
#| echo: false
#| warning: false

@@

```{r,  fig.pos: "H"}
#| label: fig-most-common-covers
#| fig-cap: "Proportion of High-rated Books by Cover Type"
#| echo: false
#| warning: false

@@

```{r,  fig.pos: "H"}
#| label: fig-page-count
#| fig-cap: "Average Page Counts of High-rated and Low-rated Books"
#| echo: false
#| warning: false

@@

```{r,  fig.pos: "H"}
#| label: fig-publish-year
#| fig-cap: "Number of Books by Publish Year and Rating Status"
#| echo: false
#| warning: false

@@

```{r,  fig.pos: "H"}
#| label: fig-rating-count
#| fig-cap: "Rating Counts by the Rating of the Book"
#| echo: false
#| warning: false

@@

```{r,  fig.pos: "H"}
#| label: tbl-book-model
#| tbl-cap: "Modeling the likelihood of a book being High-rated"
#| echo: false
#| warning: false

@@

```{r,  fig.pos: "H"}
#| label: fig-distribution
#| fig-cap: "Posterior predictive check"
#| echo: false
#| warning: false

@@

```{r,  fig.pos: "H"}
#| label: fig-post-prior
#| fig-cap: "Comparison of the prior and posterior"
#| echo: false
#| warning: false
#| 
analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
model_file <- readRDS(file = here::here("models/model.rds"))

@@

```{r,  fig.pos: "H"}
#| label: fig-trace
#| fig-cap: "Trace plot"
#| echo: false
#| fig-subcap: ["Intercept", "pages", "rating_count", "publish_year", "coverEbook", "coverKindle", "coverBoard", "coverHardcover", "coverPaperback"]
#| layout-ncol: 3
#| warning: false

@@

```{r,  fig.pos: "H"}
#| label: fig-rhat
#| fig-cap: "Rhat Plot"
#| echo: false
#| warning: false

@@

```{r,  fig.pos: "H"}
#| label: fig-interval
#| fig-cap: "90% Credibility Intervals for Predictors of High-rated Books"
#| echo: false
#| warning: false
